---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# popgencnn

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Build Status](https://travis-ci.com/mmjohn/popgencnn.svg?token=akGYX9ZmHWpGaEi1Ls7b&branch=master)](https://travis-ci.com/mmjohn/popgencnn)
[![codecov](https://codecov.io/gh/mmjohn/popgencnn/branch/master/graph/badge.svg?token=PJJ6IBM5XB)](https://codecov.io/gh/mmjohn/popgencnn)
<!-- badges: end -->

The goal of popgencnn is to support deep learning pipelines for population genomic inference in R. Current functionality supports the generation and pre-processing of simulated data sets. Specifically, coalescent simulations for use in neural networks estimators of historical population recombination rate.

## Installation

You can install popgencnn from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mmjohn/popgencnn")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(popgencnn)

ms_simulate(
  morgans_per_bp = 2.0e-8, 
  ne = 10000, 
  filename = 'sim.txt'
)

```
